---
title: "BitBayR"
author: "Michal Majka"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BitBayR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Overview

`BitBayR` is a simple R public API client to the BitBay crypto-currency exhange. 

It consists of 6 functions: `bitbay_orderbook`, `bitbay_profit`, `bitbay_trades` `bitbay_trades_from_date`, `bitbay_aggregate` and `bitbay_ticker`


Available crypto currencies: 

- `BTC` (Bitcoin)  

- `ETC`  (Ethereum)

- `LSK` (Lisk)

- `LTC` (Litecoin)

- `GAME` (Game)
                   
- `DASH` (Dash)       
                   
- `BCC` (Bitcoin cash)

Available currencies: 

- `PLN`

- `USD`

- `EUR`


# Usage


## - bitbay_orderbook

The function `bitbay_orderbook` downloads the actual order book. Its output consists of a list with two dataframes `bids` and `asks`. Each one contains three
columns `Bid` or `Ask`, `Volume` and `Price`. The price is just `Bid` or `Ask`
times the `Volume`.


```{r}
library(BitBayR)

order_book <- bitbay_orderbook(coin = "BTC", currency = "EUR")
head(order_book$bids)
head(order_book$asks)

```


## - bitbay_profit

The function `bitbay_profit` performs a theoretical/virtual market order. That is, it  theoretically sells some specific volume of a specific
crypto currency for a specific currency. In the example below one Bitcoin is sold for 
EUR assuming a prior investment of 5000€ and transaction fees 0.3%.


```{r}
bitbay_profit(coin = "BTC", amount = 1, currency = "EUR", investment = 5000, fee = 0.003)
```

## - bitbay_trades and bitbay_trades_from_date

The function `bitbay_trades` can be used to download last `n` transactions by specifying the parameter `last_trades`. In order to download all historic transactions the parameter `last_trades` can be set to `"all"`.

```{r}
last_50_trades <- bitbay_trades(coin = "BTC", currency = "EUR", last_trades = 50)
tail(last_50_trades)

```




The function `bitbay_trades_from_date` does the same task, however, it downloads all transactions occurred after a specific date. In the example below, all trades within last 3 hours.

```{r}
last_trades_3h <- bitbay_trades_from_date(coin = "BTC", currency = "EUR", 
                                           date = Sys.time() - 60 * 60 * 3)
tail(last_trades_3h)

```


## - bitbay_aggregate

The function `bitbay_aggregate` takes downloaded transactions as input as well as the time interval length (in seconds) and returns a time-series object of class `xts` with aggregated transactions. 


```{r}
aggr_data_15min <- bitbay_aggregate(last_50_trades, aggr_time = 15 * 60)
tail(aggr_data_15min)
```



## - bitbay_ticker

The function `bitbay_ticker` can be used to download a ticker for a specific pair.

```{r}
ticker_BTC_USD <- bitbay_ticker(coin = "BTC", currency = "USD")
ticker_BTC_USD
```


